---
output: rmarkdown::github_document
---

# dnsflare

Query 'Cloudflare' Domain Name System ('DNS') Servers over 'HTTPS'

## Description

Domain Name System ('DNS') queries are generally perfomed by operating
system calls when browsing the internet or making other network connectios. DNS
over 'HTTPS' services offer more local confidentiality and some 'DNS' providers
like Cloudflare offer (<https://developers.cloudflare.com/1.1.1.1/dns-over-https/json-format/>)
an 'API'-like service along with other privacy-enabled 'DNS' offerings. Tools are
provided to query this 'DNS' 'API'.

## What's Inside The Tin

The following functions are implemented:

- `query`:	Make a single DNS query
- `valid_dns_types`:	Valid DNS types

## TODO

- `batch_query()` method
- `as.data.frame()` method

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/dnsflare")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(dnsflare)

# current verison
packageVersion("dnsflare")

```

## Queries

```{r message=FALSE, warning=FALSE, error=FALSE}
query("rud.is")

query("example.com", "A")

query("microsoft.com", "MX")

# query("google-public-dns-a.google.com", "TXT") # CURRENTLY BROKEN ON CLOUDFLARE'S END

query("apple.com")

query("17.142.160.59", "PTR")
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.